### 2015-02-02 paper/conclusion.tex
minor edits

\section{Conclusion}
Through our investigation of a cell tower handoff noise model, it is clear that handoff dynamics and cellular tower density heavily influence the cellpaths measured (introducing unknown cellpaths due to reassigned cell towers) and the subsequent route flow estimate. Our results indicate that the state estimation method would benefit from an integrated model of handoff dynamics, tailored to the network at hand. Additionally, we observe that handoff dynamics have a magnified effect in denser networks, meaning that state estimation will likely less accurate. Finally, we conclude that the existing solver, which enforces a single cellpath per route, is too restrictive for the cellpaths introduced by cell tower reassignment. Relaxing this assumption will likely ameliorate the aforementioned effects. Lastly, we plan to perform a full-scale run of the route flow estimation on cellular signaling data from AT\&T in the greater Los Angeles area.

>>>>

\section{Conclusion}
Through our investigation of a cell tower handoff noise model, it is clear that handoff dynamics and cellular tower density heavily influence the measured cellpaths and subsequent route flow estimate. Our results indicate that the state estimation method would benefit from an integrated model of handoff dynamics, tailored to the network at hand. Additionally, we observe that handoff dynamics have a magnified effect in denser networks, meaning that state estimation will likely be less accurate. Finally, we conclude that the existing solver, which enforces a single cellpath per route, is too restrictive for the cellpaths introduced by cell tower reassignment. Relaxing this assumption will likely ameliorate the aforementioned effects. Lastly, we plan to perform a full-scale run of the route flow estimation on cellular signaling data from AT\&T in the greater Los Angeles area.

### 2015-02-02 paper/experiments.tex
minor edits

We present preliminary numerical results on the US experiment in Fig.~\ref{fig:results1} (more detailed slices as well as results from the CC experiment have been omitted due to space limitations). In both experiments, there is a strong positive correlation ($R=0.78$ and $R=0.74$, respectively) between the load balancing gain and flow error, caused by unknown cell paths due to reassigned cell towers. Similarly, there is a positive correlation between hysteresis and flow error as switching delays cause vehicles to skip cell tower regions along their trajectories.  This is more prominent in the denser CC experiment; in the US experiment, though, increasing hysteresis induces a dip in the flow error in the presence of other types of noise. This dip is caused by limiting jumps between towers near the borders of Voronoi regions.

>>>>

We present preliminary numerical results on the US experiment in Fig.~\ref{fig:results1} (more detailed slices as well as results from the CC experiment have been omitted due to space limitations). In both experiments, there is a strong positive correlation ($R=0.78$ and $R=0.74$, respectively) between the load balancing gain and flow error, caused by unknown cellpaths due to reassigned cell towers. Similarly, there is a positive correlation between hysteresis and flow error as switching delays cause vehicles to skip cell tower regions along their trajectories.  This is more prominent in the denser CC experiment; in the US experiment, though, increasing hysteresis induces a dip in the flow error in the presence of other types of noise. This dip is caused by limiting jumps between towers near the borders of Voronoi regions.
